---
title: 'Chapter 3: Forward Propagation'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Prediction

A good rule of thumb is to provide as much input data as a human would need to a machine to make an accurate prediction. It is important to have a good interpretation of the shape of the data before constructing a nueral network. 

Case Study: Prediction of the likelihood that a baseball team will win. 
Say you wanted to create a simple neural network that takes only on input and output producing a prediction. 

Insert diagram below. 

# Simple Neural Net

**Python**

```{python, basic neural net}
# initial weight 
weight = 0.1 

# network 
def neural_network(input, weight):
    prediction = input * weight
    return prediction
    
numb_of_toes = [8.5, 9.5, 10, 9]

input = numb_of_toes[0]

pred = neural_network(input, weight)
print (pred)
```

**R**

```{r}
# initial weight 
weight_R <- 0.1

# network
neural_networkR <- function(input, weight_R)
{
  prediction <- input * weight_R
  return(prediction)
}

numb_of_toes <- c(8.5, 9.5, 10, 9)

input <- numb_of_toes[1]

pred <- neural_networkR(input, weight_R)

pred
```

**What our network is doing?**

Go back for more notes later.



**Making a prediction with multiple inputs** 


**Python** 





**R**

```{r}
weight_sum <- function(a, b)
{
  output <- 0 
  
  output <- a %*% b
  
  return(output)
}

wghts <- c(0.1, 0.2, 0)

neural_netR2 <- function(input, wghts)
{
  pred <- weight_sum(input, wghts)
  return(pred)
}

toes <- c(8.5, 9.5, 9.9, 9.0)
wlrec <- c(0.65, 0.8, 0.8, 0.9)
nfans <- c(1.2, 1.3, 0.5, 1.0)
input <- c(toes[1], wlrec[1], nfans[1])
pred <- neural_netR2(input, wghts)

pred



```


