---
title: 'Chapter 3: Forward Propagation'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Prediction

A good rule of thumb is to provide as much input data as a human would need to a machine to make an accurate prediction. It is important to have a good interpretation of the shape of the data before constructing a nueral network. 

Case Study: Prediction of the likelihood that a baseball team will win. 
Say you wanted to create a simple neural network that takes only on input and output producing a prediction. 

Insert diagram below. 

# Simple Neural Net

*Python*
```{python, basic neural net}
weight = 0.1 

def neural_network(input, weight):
    prediction = input * weight
    return prediction
    
numb_of_toes = [8.5, 9.5, 10, 9]

input = numb_of_toes[0]

pred = neural_network(input, weight)
print (pred)
```

*R*
```{r}
weight_R <- 0.1

neural_networkR <- function(input, weight_R)
{
  prediction <- input * weight_R
  return(prediction)
}

numb_of_toes <- c(8.5, 9.5, 10, 9)

input <- numb_of_toes[1]

pred <- neural_networkR(input, weight_R)

print(pred)
```

